pirouette: Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-03-14 article.tex
Improved worksflow figure

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{workflow.png}
  \caption{
    \texttt{pirouette} pipeline. 
    The pipeline starts from a phylogeny (1a) simulated by generative prior $\mathit{P}$.
    The phylogeny is converted to an alignment (2a) using alignment model $\mathit{A}$. 
    The user supplies one or more experiments.
    For each experiment $\mathit{X}$ (a tuple of inference model $\mathit{I}$ and condition $\mathit{C}$),
    the inference model $\mathit{I}$ is used in the next step (3a),
    if the condition $\mathit{C}$ are satisfied.
    The condition $\mathit{C}$ can depend on the alignment (2a).
    The allowed inference models use the alignment (2a) 
    to create a BEAST2 posterior of (parameter estimates and) phylogenies (4a). 
    Each of the posteriors' trees is compared to the true phylogeny (1a) 
    using error measure $\mathit{E}$, 
    resulting in an error distribution (5a). 
    Optionally, a twin phylogeny (1b) can be generated from the original 
    phylogeny (1a), which then results in an error distribution (5b) 
    with similar intermediate steps.
  }
  \label{fig:pipeline}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{workflow.png}
  \caption{
    \texttt{pirouette} pipeline. 
    The pipeline starts from a phylogeny (1a) simulated by generative prior $\mathit{P}$.
    The phylogeny is converted to an alignment (2a) using alignment model $\mathit{A}$. 
    The user supplies one or more experiments.
    For each experiment $\mathit{X}$ 
    (a tuple of inference model $\mathit{I}$ and condition $\mathit{C}$),
    if its condition $\mathit{C}$ is 
    satisfied (which can depend on the alignment), 
    its inference model $\mathit{I}$ is used in the next step (3a).
    The allowed inference models use the alignment (2a) 
    to create a BEAST2 posterior of (parameter estimates and) phylogenies (4a). 
    Each of the posteriors' trees is compared to the true phylogeny (1a) 
    using error measure $\mathit{E}$, 
    resulting in an error distribution (5a). 
    Optionally, a twin phylogeny (1b) can be generated from the original 
    phylogeny (1a) using twinning parameters $T$, where $T$ may depend on
    the experiments \richel{improve}.
    From a twin phylogeny, the same intermediate steps are taken,
    resulting in a twin error distribution (5b)
  }
  \label{fig:pipeline}
\end{figure}
